Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-05-10 ms.tex
include results after doing subtraction by smoothed images on each group

In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
If uncorrected, this extra read noise will contribution 700 ppm to the time series (per frame)!
As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
We find the median of the entire image long the fast read (X) direction and subtract this from every row.
\textcolor{blue}{New Change to do it properly: We return to the reduced slope file that has reference pixels subtracted and the bias subtracted.
Here we subtract the median value from each row in each group}
In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.

\subsection{Grism Aperture}
\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.32\columnwidth]{aps_3_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_int_015_014.pdf}
\includegraphics[width=.32\columnwidth]{aps_0_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014.pdf}
\includegraphics[width=.32\columnwidth]{aps_1_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014_rowColSub.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5raw.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5red.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5redRowCol.pdf}
\caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5. As in \ref{fig:longDarkPhot}, the long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
The photometric aperture is made to represent a similar one to the F322W2 grism trace.
}\label{fig:longDarkGrism}
\end{figure*}

@@

>>>>

In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
If uncorrected, this extra read noise will contribution 700 ppm to the time series (per frame)!
As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
We find the median of the entire image long the fast read (X) direction and subtract this from every row.
\textcolor{blue}{New Change to do it properly: We return to the reduced slope file that has reference pixels subtracted and the bias subtracted.
Here we subtract the median value from each row in each group.
Doing the subtractions for each group gave an RMS that was 50 ppm smaller for aperture 0, 80 ppm larger for aperture 1 and 31 ppm smaller for aperture 3.}
In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN of all noise were uncorrelated.
The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.

\subsubsection{Grism Aperture}
\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.32\columnwidth]{aps_3_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_int_015_014.pdf}
\includegraphics[width=.32\columnwidth]{aps_0_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014.pdf}
\includegraphics[width=.32\columnwidth]{aps_1_NRCNRCALONG-DARK-72350742131_1_485_SE_2017-08-23T16h49m51_red_int_015_014_rowColSub.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5raw.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5red.pdf}
\includegraphics[width=.32\columnwidth]{long_dark_darkGrismApA5redRowCol.pdf}
\caption{Time series of a grism photometric broadband aperture during a long dark exposure for detector ALONG=A5. As in \ref{fig:longDarkPhot}, the long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
The photometric aperture is made to represent a similar one to the F322W2 grism trace.
}\label{fig:longDarkGrism}
\end{figure*}

@@

\subsubsection{Smoothed Kernel Subtraction}

We also consider more effective ways to reduce read noise than the median row subtraction discussed in Section \ref{sec:longDarks}.
We start by applying a smoothing kernel to each group (1 read for RAPID mode) up the ramp of the raw data.
The kernel is a uniform normalized kernel 1 pixel in height and 40 pixels along a row.
This enables subtraction of 1/f noise that has length scales shorter than the row length (ie timescales shorter than $\lesssim 5$ milliseconds, which the median subtraction cannot remove.

This smoothing kernel makes a dramatic improvement to the final weak lens aperture time series, as shown in Figure \ref{fig:longDarkWithRowKernel}.
The standard deviation in the time series drops from the best previous method (row and column median subtraction) by a factor of nearly 10!
For the row and column median subtraction applied to the red files, the standard deviation was 6150, 5600 and 6,600 DN for apertures 0, 1 and 2.
For the same apertures, the standard deviation in the time series drops to 650, 890 and 570 DN.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.37\columnwidth]{ap_labels_darkRedRowColSub_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.37\columnwidth]{ap_labels_darkRedsmoothedRowKernel_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedRowColSub}
\includegraphics[width=.37\columnwidth]{zoom_long_dark_darkRedsmoothedRowKernel.pdf}
\caption{The same apertures as Figure \ref{fig:longDarkPhot}, but with subtraction by a smoothed image along the rows.
Subtraction by the smoothed image has a dramatic effect on reducing correlated 1/f read noise.
}\label{fig:longDarkWithRowKernel}
\end{figure*}
